Arc Blanc: a real time ocean simulation framework

### 2025-01-31 paper.tex
Fixed cascade length and cutoff
Add a pseudo code to details the geometrical parameters definition

@@

\Framework uses by default $3$ cascades with the following settings:
\begin{itemize}
	\item $L_0 = 4$ operating for waves length $k\in [0,\frac{12\pi}{16}]$
	\item $L_1 = 16$ operating for waves length $k\in [\frac{12\pi}{16},\frac{12\pi}{256}]$
	\item $L_2 = 256$ operating for waves length $k\in [\frac{12\pi}{256},+\infty]$.
\end{itemize}

@@

The buoyancy calculation presented in Section \ref{subsubsec:buoyancy} requires the full submerged volume $v_w$ of the mesh.
\Framework uses the prism approximation similarly to the approximation proposed by Bajo \etal (2020) \cite{bajoRealisticBuoyancyModel2020a}. 
While Bajo \etal compute the submerged volume at the texel level, the same principle can be applied using triangles instead of texels using as they did the divergence theorem. 
Specifically, $v_w$ is approximated as the sum of the prisms with bases corresponding to the triangle areas $A_i$ and heights defined by the distance between the triangle centers $p_i$ and the water surface $h(x,z,t)$. 
Each term in the sum is weighted by the vertical component of the triangle normal $n_i^y$:
\begin{equation}
v_w = \sum_{T_i^s} (h(x,z,t) - p_i) A_i n_i^y.
\end{equation}
Note that this formula is correct only under the assumption that the mesh is closed.

>>>>

\usepackage{algorithm}
\usepackage{algpseudocode}
\algrenewcommand{\algorithmiccomment}[1]{\hfill \textcolor{greenF}{// #1}}

@@

\Framework uses by default $3$ cascades with the following settings:
\begin{itemize}
	\item $L_0 = 256$ operating for waves length $k\in [0,\frac{12\pi}{16}]$
	\item $L_1 = 16$ operating for waves length $k\in [\frac{12\pi}{16},\frac{12\pi}{4}]$
	\item $L_2 = 4$ operating for waves length $k\in [\frac{12\pi}{4},+\infty]$.
\end{itemize}

@@

The buoyancy calculation presented in Section \ref{subsubsec:buoyancy} requires the full submerged volume $v_w$ of the mesh.
\Framework uses the prism approximation similarly to the approximation proposed by Bajo \etal (2020) \cite{bajoRealisticBuoyancyModel2020a}. 
While Bajo \etal compute the submerged volume at the texel level, the same principle can be applied using triangles instead of texels using as they did the divergence theorem. 
Specifically, $v_w$ is approximated as the sum of the prisms with bases corresponding to the triangle areas $A_i$ and heights defined by the distance $d_i$ between the triangle centers $p_i$ and the water surface $h(p_i,t)$. 
Each term in the sum is weighted by the vertical component of the triangle normal $n_i^y$:
\begin{equation}
v_w = \sum_{T_i^s} A_i d_i n_i^y.
\end{equation}
Note that this formula is correct only under the assumption that the mesh is closed.

The pseudo code for the calculations performed in this section can be read in the Algorithm \ref{alg:geom_params}.

\input{Algorithms/geometrical_parameters.tex}
